---
title: "Housing Price Predictions - EDA"
author: "Divya Reddy"
date: "9/25/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Load packages
```{r}
library(dplyr)
library(ggplot2)
```

Set present working directory and load the data 
```{r}
setwd("C:/Users/dreddy/Desktop/HousingData")
housing <- read.csv("./train.csv")
```

Looking at the datatypes of the variables 
```{r}
str(housing)
```

After looking at the datatypes and going through the data_description.txt, we need to convert the following columns to character datatype

```{r}
housing$MSSubClass <- as.character(housing$MSSubClass)
housing$YearBuilt <- as.character(housing$YearBuilt)
housing$YearRemodAdd <- as.character(housing$YearRemodAdd)
housing$MoSold <- as.character(housing$MoSold)
housing$YrSold <- as.character(housing$YrSold)
housing$GarageYrBlt <- as.character(housing$GarageYrBlt)
#str(housing)
```
Looking at the summary of the dataset
#```{r}
#summary(housing)
#```

Identify the numeric columns to check for outliers
```{r}
colnames(dplyr::select_if(housing, is.numeric))
```

Plotting graphs for outlier analysis
```{r}
boxplot(housing$LotFrontage, ylab = "Lot Frontage", main = "Boxplot for Lot Frontage")
boxplot(housing$LotArea, ylab = "Lot Area", main = "Boxplot for Lot Area")
boxplot(housing$OverallQual, ylab = "Quality", main = "Over all Quality")
boxplot(housing$OverallCond, ylab = "Quality", main = "Over all Condition")
boxplot(housing$MasVnrArea, ylab = "Masonry Area", main = "Masonry venner area")
boxplot(housing$BsmtFinSF1, ylab = "Basement Type1 Area", main = "Basement Type 1 Area")
boxplot(housing$BsmtFinSF2, ylab = "Basement Type2 Area", main = "Basement Type 2 Area")
boxplot(housing$BsmtUnfSF, ylab = "Basement unfinished Area", main = "Basement Unfinished Area")
boxplot(housing$TotalBsmtSF, ylab = "Basement Area", main = "Total Basement Area")
boxplot(housing$X1stFlrSF, ylab = "1st floor sq ft", main = "!st floor Area")
boxplot(housing$X2ndFlrSF, ylab = "2nd floor sq ft", main = "2nd floor Area")
boxplot(housing$LowQualFinSF, ylab = "Low quality finish sq ft", main = "Low quality finish sq ft")
boxplot(housing$GrLivArea)
boxplot(housing$BsmtFullBath)
boxplot(housing$BsmtHalfBath)
boxplot(housing$FullBath)
boxplot(housing$HalfBath)
boxplot(housing$BedroomAbvGr)
boxplot(housing$KitchenAbvGr)
boxplot(housing$TotRmsAbvGrd)
boxplot(housing$Fireplaces)
boxplot(housing$GarageCars)
boxplot(housing$GarageArea)
boxplot(housing$WoodDeckSF)
boxplot(housing$OpenPorchSF)
boxplot(housing$EnclosedPorch)
boxplot(housing$X3SsnPorch)
boxplot(housing$ScreenPorch)
boxplot(housing$PoolArea)
boxplot(housing$MiscVal)
boxplot(housing$SalePrice)
```
