---
title: "Housing Predictions - EDA [Day3]"
author: "Divya Reddy"
date: "9/26/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages
```{r}
library(dplyr)
library(ggplot2)
library(data.table)
```

Set present working directory and load the data 
```{r}
setwd("C:/Users/dreddy/Desktop/HousingData")
housing <- read.csv("./train.csv")
```

Convert data frame to data table
```{r}
housing <- setDT(housing)
```

Looking at the datatypes of the variables 
```{r}
str(housing)
```

After looking at the datatypes and going through the data_description.txt, we need to convert the following columns to character datatype

```{r}
housing$MSSubClass <- as.character(housing$MSSubClass)
housing$YearBuilt <- as.character(housing$YearBuilt)
housing$YearRemodAdd <- as.character(housing$YearRemodAdd)
housing$MoSold <- as.character(housing$MoSold)
housing$YrSold <- as.character(housing$YrSold)
housing$GarageYrBlt <- as.character(housing$GarageYrBlt)
#str(housing)
```

Outliers can be identified by using boxplots, boxplots(IQR) or using Z scores. 
The boxplot(IQR) method using the 1.5xIQR- Q1 (lower limit) and Q3+ 1.5xIQR (upper limit) to eliminate outliers
The z-score value is the measure of how far the data point is from the mean = 0 and SD = 1, i.e., a normal deviation. We consider the z scores between -3 to 3 to eliminate outliers.
You can also remove all outliers less than the 5th percentile and greater than the 95th percentile


Plotting graphs for outlier analysis
```{r}
varlist <- colnames(dplyr::select_if(housing, is.numeric))

plot <- function (varlist) {
   # require(ggplot2)
    ggplot(data = housing, mapping = aes_string(y=varlist))+
            geom_boxplot() + scale_x_discrete(limits=c("0.5", "1"))
}
```

```{r}
lapply(varlist, FUN = plot)
```

Display the outliers using boxplot.stats and by using the 5th and 95th percentile
```{r}
boxplot.stats(housing$Fireplaces)$out
select(housing,Fireplaces) %>% filter(Fireplaces > quantile(housing$Fireplaces, 0.05),Fireplaces > quantile(housing$Fireplaces, 0.95))
```
